aircraft-pfp

### 2024-08-22 examples/aircraft-flask.Rmd
add plots to articles

```{r obs_plotsave, fig.width=7, fig.height=5, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_aircraftflask.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

>>>>

```{r obs_plotsave, fig.width=5, fig.height=3, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_aircraftflask.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

```{r savesf, fig.width=5, fig.height=3, eval = T, echo = F}
library(sf)
x <- st_as_sf(df3, coords = c("longitude", "latitude"), crs = 4326)
png("../man/figures/obsplot_aircraftflask_map.png", width = 1500, height = 1000, res = 200)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
dev.off()
```

```{r sf, fig.width=7, fig.height=5, eval = F}
library(sf)
x <- st_as_sf(df3, coords = c("longitude", "latitude"), crs = 4326)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
```

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_aircraftflask_map.png?raw=true)

### 2024-08-22 examples/aircraft-pfp.Rmd
add plots to articles

```{r obs_plotsave, fig.width=7, fig.height=5, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_aircraftpfp.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

```{r obs_plot, fig.width=7, fig.height=5, eval = F}
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
```

@@

```{r savesf, fig.width=7, fig.height=5, eval = T, echo = F}
library(sf)
x <- st_as_sf(df3, coords = c("longitude", "latitude"), crs = 4326)
png("../man/figures/obsplot_aircraftpfp_map.png", width = 1500, height = 1000, res = 200)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
dev.off()
```

```{r sf, fig.width=7, fig.height=5, eval = F}
library(sf)
x <- st_as_sf(df3, coords = c("longitude", "latitude"), crs = 4326)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
```

>>>>

```{r obs_plotsave, fig.width=5, fig.height=3, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_aircraftpfp.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

```{r obs_plot, fig.width=5, fig.height=3, eval = F}
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
```

@@

```{r savesf, fig.width=5, fig.height=3, eval = T, echo = F}
library(sf)
x <- st_as_sf(df3, coords = c("longitude", "latitude"), crs = 4326)
png("../man/figures/obsplot_aircraftpfp_map.png", width = 1500, height = 1000, res = 200)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
dev.off()
```

```{r sf, fig.width=5, fig.height=3, eval = F}
library(sf)
x <- st_as_sf(df3, coords = c("longitude", "latitude"), crs = 4326)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
```
